---
title: "SURV615 HW2"
author: "Xiaoqing Liu"
date: "2024-09-11"
output: html_document
---

```{r setup, include=FALSE, tidy=TRUE}
knitr::opts_chunk$set(echo = TRUE,cache=TRUE, 
                      autodep=TRUE, cache.comments=FALSE,
                      message=FALSE, warning=FALSE)
```

1. Using the Auto dataset in the ISLR2 package fit a regression model of miles per gallon (mpg) as a function of acceleration and save as an object called “mod1”.
```{r}
library(ISLR2)
mod1 <- lm(mpg~acceleration, data = Auto)
summary(mod1)
```

2. How would you interpret the intercept and slope from #1?

When acceleration is 0, the estimated value of mpg is 4.8332.But this is not realistic or practically significant. The slope indicated that for every one-unit increase in acceleration, the miles per gallon (mpg) increases by approximately 1.20.


3. Does the intercept make sense? Show how you would refit the model to get an interpretable intercept and explain whether this is necessary. Interpret the intercept from the refit model.

No, because an acceleration of 0 is unrealistic for a car. 
```{r}
Auto$acceleration_centered <- Auto$acceleration - mean(Auto$acceleration)
mod1_centered <- lm(mpg ~ acceleration_centered, data = Auto)
summary(mod1_centered)
```

4. What is the null hypothesis being tested via the t statistic for acceleration? Does this hypothesis change if the predictor is centered?

Under the null hypothesis, changes in acceleration do not have a statistically significant effect on mpg.
the hypothesis does not change if the predictor is centered. Because the null hypothesis and the t-test on the slope are unaffected by centering the predictor, only the interpretation of the intercept changes.


5. What are some of the reasons you might choose a more flexible modeling approach? What are some of the tradeoffs of choosing a more flexible approach?

Choosing a more flexible modeling approach can improve accuracy and better capture complex
relationships,this can lead to improved predictive accuracy.However, the tradeoff is that flexible models often become less interpretable, making it difficult to understand the specific relationships between variables. 


